Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-04-16 mpaper/paper.tex
A bit more refactoring

\begin{lemma} \label{lemma:integral_of_r}
  \[
    \int \lVert \mathbf{r} \rVert_\infty q(\mathbf{r} \mid
    \mathbf{u})\,\mathrm{d}\mathbf{r} \le a + \lVert \mathbf{Su} \rVert_1,
  \]
  where $a$ is a constant independent of $\mathbf{u}$.
\end{lemma}
\begin{proof}
  Since $\rinf \le \lVert \mathbf{r} \rVert_1$,
  \[
    \int \lVert \mathbf{r} \rVert_\infty q(\mathbf{r} \mid
    \mathbf{u})\,\mathrm{d}\mathbf{r} \le \int \lVert \mathbf{r} \rVert_1
    q(\mathbf{r} \mid \mathbf{u})\,\mathrm{d}\mathbf{r} =
    \sum_{i=1}^{|\mathcal{S}|} \mathbb{E}[|r_i|].
  \]
  As each $\mathbb{E}[|r_i|]$ is a mean of a folded Gaussian distribution,
  \[
    \mathbb{E}[|r_i|] = \sigma_i \sqrt{\frac{2}{\pi}} \exp
    \left(-\frac{\xi_i^2}{2\sigma_i^2} \right) + \xi_i \left( 1 - 2\Phi \left(
        -\frac{\xi_1}{\sigma_1} \right) \right),
  \]
  where $\xi_i = \left[\mathbf{Su}\right]_i$, $\sigma_i =
  \sqrt{\bm\Gamma_{i,i}}$\footnote{The expression
    under the square root sign is non-negative because $\bm\Gamma$ is a
    covariance matrix of a Gaussian distribution, hence also positive
    semi-definite, which means that its diagonal entries are non-negative.}, and
  $\Phi$ is the cumulative distribution function of the standard Gaussian.
  Furthermore,
  \[
    \mathbb{E}[|r_i|] \le \sigma_i\sqrt{\frac{2}{\pi}} + |\xi_i|,
  \]
  as $\sigma_i$ is non-negative, and $\Phi(x) \in [0, 1]$ for all $x$. Since
  \[
    \sum_{i=1}^{|\mathcal{S}|} |\xi_i| = \lVert \mathbf{Su} \rVert_1,
  \]
  we can set
  \[ a = \sum_{i=1}^{|\mathcal{S}|} \sigma_i \sqrt{\frac{2}{\pi}} \]
  to get the desired result.
\end{proof}

>>>>

\begin{lemma} \label{lemma:integral_of_r}
  \[
    \int \lVert \mathbf{r} \rVert_\infty q(\mathbf{r} \mid
    \mathbf{u})\,\mathrm{d}\mathbf{r} \le a + \lVert \mathbf{Su} \rVert_1,
  \]
  where $a$ is a constant independent of $\mathbf{u}$.
\end{lemma}
\begin{proof}
  Since $\rinf \le \lVert \mathbf{r} \rVert_1$,
  \[
    \int \lVert \mathbf{r} \rVert_\infty q(\mathbf{r} \mid
    \mathbf{u})\,\mathrm{d}\mathbf{r} \le \int \lVert \mathbf{r} \rVert_1
    q(\mathbf{r} \mid \mathbf{u})\,\mathrm{d}\mathbf{r} =
    \sum_{i=1}^{|\mathcal{S}|} \mathbb{E}[|r_i|].
  \]
  As each $\mathbb{E}[|r_i|]$ is a mean of a folded Gaussian distribution,
  \[
    \mathbb{E}[|r_i|] = \sigma_i \sqrt{\frac{2}{\pi}} \exp
    \left(-\frac{\xi_i^2}{2\sigma_i^2} \right) + \xi_i \left( 1 - 2\Phi \left(
        -\frac{\xi_1}{\sigma_1} \right) \right),
  \]
  where $\xi_i = \left[\mathbf{Su}\right]_i$, $\sigma_i =
  \sqrt{\Gamma_{i,i}}$\footnote{The diagonal of $\bm\Gamma$ is non-negative
    because $\bm\Gamma$ is a covariance matrix of a Gaussian distribution, hence
    also positive semi-definite.}, and $\Phi$ is the cumulative distribution
  function of the standard Gaussian. Furthermore,
  \[
    \mathbb{E}[|r_i|] \le \sigma_i\sqrt{\frac{2}{\pi}} + |\xi_i|,
  \]
  as $\sigma_i$ is non-negative, and $\Phi(x) \in [0, 1]$ for all $x$. Since
  \[
    \sum_{i=1}^{|\mathcal{S}|} |\xi_i| = \lVert \mathbf{Su} \rVert_1,
  \]
  we can set
  \[ a = \sum_{i=1}^{|\mathcal{S}|} \sigma_i \sqrt{\frac{2}{\pi}} \]
  to get the desired result.
\end{proof}
